A Combinatorial Search of Parameterized Quantum Circuit Learning for Quantum Chemical Applications

### 2025-03-04 manuscript/main.tex
update flow

\setcounter{secnumdepth}{1}
\section{Introduction}
[Problem: QML methods related to quantum chemistry are rarely studied so we chose two different sets of data, one that's classical in-quantum out and the other that is quantum in-quantum out]

@@

\subsection{DDCC}

>>>>

\setcounter{secnumdepth}{1}
\section{Introduction}
Four paragraph structure:
\begin{itemize}
	\item General problem and classical machine learning 
	\item quantum computing and qml
	\item Parameterized quantum circuits
	\item What we introduce
\end{itemize}

[Problem: QML methods related to quantum chemistry are rarely studied so we chose two different sets of data, one that's classical in-quantum out and the other that is quantum in-quantum out]

@@

\subsection{DDCC}
Structure
\begin{itemize}
	\item Broad set
	\item RUD/AL tests
	\item learning curve (maybe)
	\item real device 
\end{itemize}
